Project Proposal

### 2024-11-17 CURJ_IDS702Projectproposal.qmd
finished cleaning merged data

all_states_final[sample(nrow(all_states_final), 10), c('State', 'County', 'School.Funding.Adequacy', 'Region', 'School.Funding.Cat')]
```
```{r}

>>>>

all_states_final[sample(nrow(all_states_final), 10), c('State', 'County', 'School.Funding.Adequacy', 'Region', 'School.Funding.Cat')]
```
```{r}
acs_proptax <- read.csv('https://raw.githubusercontent.com/wujenny214/F24_STATS_FINAL/refs/heads/main/county_data/acs_proptax.csv')
merged_data_full <- merge(acs_proptax, all_states_final, by = "FIPS")
merged_data_full <- select(merged_data_full, -c(6, 7))
```
